---
title: "Assessment 3.rmd"
author: "Shaikh muskaan salim  s4660123"
date: "17/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r cars}
#install.packages("webshot")
#install.packages("stringr")
#install.packages("treemapify")
#install.packages("ggridges")



```

## LOad Library

You can also embed plots, for example:

```{r pressure, echo=FALSE}

library(tidyverse)
library(skimr)
library(RColorBrewer)
library(networkD3)
library(htmlwidgets)
library(waffle)
library(lubridate)
library(Hmisc)
library(viridis)
library(plotly)
library(stringr)
library(treemapify)
library(ggridges)

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


# DATA Loading

```{r}

animal_outcomes <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-21/animal_outcomes.csv')
animal_complaints <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-21/animal_complaints.csv')
brisbane_complaints <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-21/brisbane_complaints.csv')
```

The analysis is using 3 different datasets as following
a) Animal Outcomes
b) Animal Complaints
c) Brisbane Complaints


# PART1 - Animal Outcome

```{r}
dim(animal_outcomes)
```
Animal outcome dataset is having 664 rows and 12 columns

```{r}
AO = animal_outcomes %>% mutate_at(vars(year,animal_type,outcome), list(factor))
skim(AO)
```
```{r}

Intake_AO = animal_outcomes %>% group_by(animal_type,year) %>% tally(Total) %>% ggplot(aes(x= year, y = n, group = animal_type, color=animal_type)) + geom_line() + geom_point() + theme(legend.position="top") +  labs(x="Year", y="Intake count", title="Different Type Animal intake by Year", subtitle= "RSPCA Australia Animal Outcomes 1999-2018")
Intake_AO
```
The above graph shows animal intake count over the years


```{r}
dim(animal_outcomes)

```


```{r}
cd_int = animal_outcomes %>% filter(animal_type == "Dogs" | animal_type == "Cats"| animal_type == "Wildlife") %>% group_by(animal_type,year) %>% tally(Total) %>% mutate_at(vars(year,animal_type), list(factor)) %>% as.data.frame()

cd_eth = animal_outcomes %>% filter(animal_type == "Dogs" | animal_type == "Cats"| animal_type == "Wildlife") %>% filter(outcome=="Euthanized") %>% group_by(animal_type,year, outcome) %>% tally(Total) %>% mutate_at(vars(year,animal_type,outcome), list(factor)) %>% as.data.frame() 

cd_reh = animal_outcomes %>% filter(animal_type == "Dogs" | animal_type == "Cats"| animal_type == "Wildlife") %>% filter(outcome=="Rehomed") %>% group_by(animal_type,year, outcome) %>% tally(Total) %>% mutate_at(vars(year,animal_type,outcome), list(factor)) %>% as.data.frame()
```

```{r}
cd_int$euth_por= ((cd_eth$n/cd_int$n))
cd_int %>% filter(animal_type == "Dogs")
```
```{r}
cd_int$euth_por= ((cd_eth$n/cd_int$n))
cd_int %>% filter(animal_type == "Cats")
```
```{r}
cd_int$euth_por= ((cd_eth$n/cd_int$n))
cd_int %>% filter(animal_type == "Wildlife")
```










#PART 2 - Animal Complaints



```{r}

colnames(animal_complaints)
```

```{r}
dim(animal_complaints)
```
There are 42413 rows and 7 columns in the dataset

```{r}
animal_complaints$Year = str_extract(animal_complaints$`Date Received`,"\\w+$")

animal_complaints$Month = str_extract(animal_complaints$`Date Received`,"(\\w+)")
head(animal_complaints)
```
Dataset is updated with Separate Year  & Month fields

```{r}
AC = animal_complaints 
skim(AC)
```


```{r}


animal_complaints$Year = as.numeric(animal_complaints$Year)
head(animal_complaints)
```


```{r}
#bp1 = ggplot(AC) + geom_bar(aes(x=Year, fill= `Complaint Type`)) + facet_wrap(~`Animal Type`, nrow=2) + theme_classic() + scale_fill_brewer(palette="Dark2") + labs(x="Year(date recieved)", y = "Count", title= "Complaints over the years", subtitle= "Animal Complaints 2013 to 2020")

bp1 = ggplot(AC) + geom_bar(aes(x=Year, color=`Complaint Type`))   + labs(x="Year(date recieved)", y = "Count", title= "Complaints over the years", subtitle= "Animal Complaints 2013 to 2020")
bp1
```






# Part 3 : Brisbane Animal Complaint




```{r}
brisbane_complaints$yearquarter = brisbane_complaints$date_range
unique(brisbane_complaints$date_range)
```



```{r}

dim(brisbane_complaints)
```
Brisbane Dataset is having 31330 rows and 8 columns in total

```{r}
brisbane_complaints$yearquarter = str_replace_all(brisbane_complaints$yearquarter, "1st-quarter-2016-17.csv", "2016-Q1")
brisbane_complaints$yearquarter = str_replace_all(brisbane_complaints$yearquarter, "apr-jun-2019.csv", "2019-Q2")
brisbane_complaints$yearquarter = str_replace_all(brisbane_complaints$yearquarter, "apr-to-jun-2018.csv", "2018-Q2")
brisbane_complaints$yearquarter = str_replace_all(brisbane_complaints$yearquarter, "april-june-2016.csv", "2016-Q2")
brisbane_complaints$yearquarter = str_replace_all(brisbane_complaints$yearquarter, "april-to-june-2017.csv", "2017-Q2")
brisbane_complaints$yearquarter = str_replace_all(brisbane_complaints$yearquarter, "cars-srsa-open-data-animal-related-complaints-apr-to-jun-2020.csv", "2020-Q2")
brisbane_complaints$yearquarter = str_replace_all(brisbane_complaints$yearquarter, "cars-srsa-open-data-animal-related-complaints-jan-to-mar-2020.csv", "2020-Q1")
brisbane_complaints$yearquarter = str_replace_all(brisbane_complaints$yearquarter, "cars-srsa-open-data-animal-related-complaints-oct-to-dec-2019.csv", "2019-Q4")
brisbane_complaints$yearquarter = str_replace_all(brisbane_complaints$yearquarter, "jan-mar-2019.csv", "2019-Q1")
brisbane_complaints$yearquarter = str_replace_all(brisbane_complaints$yearquarter, "jan-to-mar-2018.csv", "2018-Q1")
brisbane_complaints$yearquarter = str_replace_all(brisbane_complaints$yearquarter, "january-to-march-2017.csv", "2017-Q1")
brisbane_complaints$yearquarter = str_replace_all(brisbane_complaints$yearquarter, "jul-to-sep-2018.csv", "2018-Q3")
brisbane_complaints$yearquarter = str_replace_all(brisbane_complaints$yearquarter, "july-to-september-2017.csv", "2017-Q3")
brisbane_complaints$yearquarter = str_replace_all(brisbane_complaints$yearquarter, "jul-to-sep-2019.csv", "2017-Q3")
brisbane_complaints$yearquarter = str_replace_all(brisbane_complaints$yearquarter, "oct-to-dec-2018.csv", "2018-Q4")
brisbane_complaints$yearquarter = str_replace_all(brisbane_complaints$yearquarter, "october-to-december-2016.csv", "2016-Q4")
brisbane_complaints$yearquarter = str_replace_all(brisbane_complaints$yearquarter, "october-to-december-2017.csv", "2017-Q4")
sort(unique(brisbane_complaints$yearquarter),decreasing=FALSE)
```
```{r}

```

```{r}
sum(is.na(brisbane_complaints$responsible_office))
```
Responsible office field is having majority of values as null and so this field can omitted for our calculation

```{r}
BC= subset(brisbane_complaints, select=-c(responsible_office, date_range, nature, city))

sort(unique(BC$yearquarter),decreasing=FALSE)
```
```{r}
BC = BC %>% mutate_at(vars(animal_type,category,suburb, yearquarter),list(factor))
summary(BC)
```



```{r}
bv2= BC %>% group_by(animal_type) %>% tally() %>% ggplot(aes(x=animal_type, y=n)) +  geom_bar(stat="identity") + labs(x="Animal types", y = "Count", title= "Animal Types", subtitle= "Brisbane Animal Complaints Jan 2016 to June 2020")
bv2
```
```{r}
# Number of complaints throughout the quarters
bv3= BC %>% group_by(yearquarter) %>% tally() %>% ggplot(aes(x=yearquarter, y=n, group=1)) + geom_line() + geom_point() + labs(x = "Year-quarter", y = "Number of complaints", title = "Number of complaints throughout the quarters",subtitle= "Brisbane Animal Complaints Jan 2017 to June 2020")
bv3

```



